An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-30 draft.tex
Captions added

\usepackage{lineno,hyperref}
\usepackage{rotating}
\usepackage{algpseudocode,algorithm}
\usepackage{hyperref}
\usepackage{listings}

@@

@@

This paper has been supported in part by projects DeepBio
(TIN2017-85727-C4-2-P).

>>>>

\usepackage{lineno,hyperref}
\usepackage{rotating}
\usepackage{algpseudocode,algorithm}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}

@@

\begin{figure*}[h!tb]
    \begin{tabular}
        {c@{\hspace*{-0.00001\textwidth}}
         c@{\hspace*{-0.00001\textwidth}}
         c@{\hspace*{-0.00001\textwidth}}
        }
    GA  &  PSO & GA \& PSO\\   
    \includegraphics[width=0.33\textwidth]{GAOnly_f001}&
    \includegraphics[width=0.33\textwidth]{PSOOnly_f001}&
    \includegraphics[width=0.33\textwidth]{GAPSO_f001}\\

    \includegraphics[width=0.33\textwidth]{GAOnly_f002}&
    \includegraphics[width=0.33\textwidth]{PSOOnly_f002}&
    \includegraphics[width=0.33\textwidth]{GAPSO_f002}\\

    \includegraphics[width=0.33\textwidth]{GAOnly_f003}&
    \includegraphics[width=0.33\textwidth]{PSOOnly_f003}&
    \includegraphics[width=0.33\textwidth]{GAPSO_f003}\\

    \includegraphics[width=0.33\textwidth]{GAOnly_f004}&
    \includegraphics[width=0.33\textwidth]{PSOOnly_f004}&
    \includegraphics[width=0.33\textwidth]{GAPSO_f004}\\

    \includegraphics[width=0.33\textwidth]{GAOnly_f005}&
    \includegraphics[width=0.33\textwidth]{PSOOnly_f005}&
    \includegraphics[width=0.33\textwidth]{GAPSO_f005}\\
    \end{tabular}
    \vspace{-3ex}
     \caption{
 Scaling of runtime with dimension to reach certain target values $\Delta f$. Lines:
 average runtime (aRT); Cross ($+$): median runtime of successful runs to reach
 the most difficult target that was reached at least once (but not always);
 Cross (\textcolor{red}{$\times$}): maximum number of f-evaluations in any trial. Notched boxes:
 interquartile range with median of simulated runs; All values are divided by
 dimension and plotted as $log_{10}$ values versus dimension. 
 %Shown is the aRT for
 %fixed values of $\Delta f = 10k$ with $k$ given in the legend. 
 Numbers above aRT-symbols
 (if appearing) indicate the number of trials reaching the respective target.
 %The light thick line with diamonds indicates the best algorithm from BBOB 2009
 %for the most difficult target. Horizontal lines mean linear scaling, slanted
 %grid lines depict quadratic scaling.
 }
    \end{figure*}

    \begin{figure}[h!tb]
        \begin{tabular}
            {c@{\hspace*{-0.00001\textwidth}}
             c@{\hspace*{-0.00001\textwidth}}
            }

        \includegraphics[width=0.48\textwidth]{ppfigs_f001}&
        \includegraphics[width=0.48\textwidth]{ppfigs_f002}\\

        \includegraphics[width=0.48\textwidth]{ppfigs_f003}&
        \includegraphics[width=0.48\textwidth]{ppfigs_f004}\\

        \includegraphics[width=0.48\textwidth]{ppfigs_f005}&
        \\
        \end{tabular}
        \vspace{-3ex}
         \caption{Average running time (aRT in number of f-evaluations as $log_{10}$ value),
          divided by dimension for target function value $10^{-8}$ versus dimension. 
          Slanted grid lines indicate quadratic scaling with the dimension. 
          Different symbols correspond to different algorithms given in the 
          legend of $f_1$. Light symbols give the maximum number of 
          function evaluations from the longest trial divided by dimension. 
          Black stars indicate a statistically better result compared to 
          all other algorithms with $p < 0.01$ and Bonferroni 
          correction number of dimensions (six).}
    \end{figure}

@@

This paper has been supported in part by projects TecNM-5654.19-P and DeepBio
(TIN2017-85727-C4-2-P).
